\myfont Implementation and evaluation of register allocation for translating LLVM-{}- to x86-64

### 2024-01-13 article.tex
explain sha256

\subsubsection{\lstinline!benches/sha256.ll!}
\begin{table}[H]
\makebox[\textwidth][c]{
\begin{NiceTabular}{|c|cccccccc|}
\hline
n & clang & simple 12 & simple 2 & briggs 12 & briggs 2 & linear & greedy 12 & greedy 0 \\
\hline
100 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00000x& \cellcolor[rgb]{0.9990234375,0.9619140625,0.75} 3.17253x& \cellcolor[rgb]{0.9990234375,0.9560546875,0.75} 3.35873x& \cellcolor[rgb]{0.9990234375,0.9619140625,0.75} 3.17637x& \cellcolor[rgb]{0.9990234375,0.9560546875,0.75} 3.37014x& \cellcolor[rgb]{0.9990234375,0.75,0.75} 19.50758x& \cellcolor[rgb]{0.9990234375,0.75,0.75} 19.44391x& \cellcolor[rgb]{0.9990234375,0.75,0.75} 19.61921x\\
1000 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00000x& \cellcolor[rgb]{0.9990234375,0.9189453125,0.75} 4.54197x& \cellcolor[rgb]{0.9990234375,0.91015625,0.75} 4.83710x& \cellcolor[rgb]{0.9990234375,0.9189453125,0.75} 4.54593x& \cellcolor[rgb]{0.9990234375,0.91015625,0.75} 4.83359x& \cellcolor[rgb]{0.9990234375,0.75,0.75} 31.35583x& \cellcolor[rgb]{0.9990234375,0.75,0.75} 31.26454x& \cellcolor[rgb]{0.9990234375,0.75,0.75} 31.56475x\\
10000 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00000x& \cellcolor[rgb]{0.9990234375,0.9111328125,0.75} 4.80821x& \cellcolor[rgb]{0.9990234375,0.9013671875,0.75} 5.11478x& \cellcolor[rgb]{0.9990234375,0.9111328125,0.75} 4.80648x& \cellcolor[rgb]{0.9990234375,0.9013671875,0.75} 5.12019x& \cellcolor[rgb]{0.9990234375,0.75,0.75} 33.50659x& \cellcolor[rgb]{0.9990234375,0.75,0.75} 33.41428x& \cellcolor[rgb]{0.9990234375,0.75,0.75} 33.72138x\\
\hline
\end{NiceTabular}}
\caption{\label{tab:sha256}Benchmark of \texttt{benches/sha256.ll} output by \mintinline{bash}{dune exec bench -- -f fib -n 1000}}
\end{table}

@@

>>>>

\subsubsection{\lstinline!benches/sha256.ll!}
The sha256 benchmark is a massive program when compared to all others. It stems from an MIT licensed implementation  \cite{sha256}. The core function is \texttt{sha256\_compress} with no loops, but it does perform 64 SHA-2 rounds which are quite involved by design. As most binary operations depend on \~5 or so instructions instead of 1-2 as is possible for the majority, that alone ought to reduce performance immensely.
4 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 151231& \cellcolor[rgb]{0.810546875,0.9990234375,0.75} 1.24623x& \cellcolor[rgb]{0.8193359375,0.9990234375,0.75} 1.28026x& \cellcolor[rgb]{0.8115234375,0.9990234375,0.75} 1.24897x& \cellcolor[rgb]{0.8193359375,0.9990234375,0.75} 1.28066x& \cellcolor[rgb]{0.9619140625,0.9990234375,0.75} 1.85133x& \cellcolor[rgb]{0.96875,0.9990234375,0.75} 1.88049x& \cellcolor[rgb]{0.9990234375,0.966796875,0.75} 3.00814x& \cellcolor[rgb]{0.9990234375,0.966796875,0.75} 3.02968x\\
8 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 159289& \cellcolor[rgb]{0.8515625,0.9990234375,0.75} 1.41012x& \cellcolor[rgb]{0.8623046875,0.9990234375,0.75} 1.45279x& \cellcolor[rgb]{0.8525390625,0.9990234375,0.75} 1.41295x& \cellcolor[rgb]{0.861328125,0.9990234375,0.75} 1.44789x& \cellcolor[rgb]{0.9990234375,0.9853515625,0.75} 2.42693x& \cellcolor[rgb]{0.9990234375,0.984375,0.75} 2.46595x& \cellcolor[rgb]{0.9990234375,0.923828125,0.75} 4.38812x& \cellcolor[rgb]{0.9990234375,0.923828125,0.75} 4.40305x\\
16 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 173067& \cellcolor[rgb]{0.92578125,0.9990234375,0.75} 1.70848x& \cellcolor[rgb]{0.94140625,0.9990234375,0.75} 1.76986x& \cellcolor[rgb]{0.92578125,0.9990234375,0.75} 1.70898x& \cellcolor[rgb]{0.94140625,0.9990234375,0.75} 1.77111x& \cellcolor[rgb]{0.9990234375,0.953125,0.75} 3.45499x& \cellcolor[rgb]{0.9990234375,0.9521484375,0.75} 3.49756x& \cellcolor[rgb]{0.9990234375,0.8466796875,0.75} 6.88402x& \cellcolor[rgb]{0.9990234375,0.8466796875,0.75} 6.88614x\\
32 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 202474& \cellcolor[rgb]{0.9990234375,0.994140625,0.75} 2.15587x& \cellcolor[rgb]{0.9990234375,0.990234375,0.75} 2.25675x& \cellcolor[rgb]{0.9990234375,0.994140625,0.75} 2.14418x& \cellcolor[rgb]{0.9990234375,0.990234375,0.75} 2.26214x& \cellcolor[rgb]{0.9990234375,0.904296875,0.75} 5.03392x& \cellcolor[rgb]{0.9990234375,0.9013671875,0.75} 5.12076x& \cellcolor[rgb]{0.9990234375,0.75,0.75} 10.69747x& \cellcolor[rgb]{0.9990234375,0.75,0.75} 10.70125x\\
64 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 256682& \cellcolor[rgb]{0.9990234375,0.9736328125,0.75} 2.78746x& \cellcolor[rgb]{0.9990234375,0.96875,0.75} 2.95124x& \cellcolor[rgb]{0.9990234375,0.9736328125,0.75} 2.79279x& \cellcolor[rgb]{0.9990234375,0.96875,0.75} 2.95499x& \cellcolor[rgb]{0.9990234375,0.8349609375,0.75} 7.25491x& \cellcolor[rgb]{0.9990234375,0.830078125,0.75} 7.39688x& \cellcolor[rgb]{0.9990234375,0.75,0.75} 16.05447x& \cellcolor[rgb]{0.9990234375,0.75,0.75} 16.05908x\\
128 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 369901& \cellcolor[rgb]{0.9990234375,0.953125,0.75} 3.45784x& \cellcolor[rgb]{0.9990234375,0.9462890625,0.75} 3.67742x& \cellcolor[rgb]{0.9990234375,0.953125,0.75} 3.45438x& \cellcolor[rgb]{0.9990234375,0.9462890625,0.75} 3.67655x& \cellcolor[rgb]{0.9990234375,0.7626953125,0.75} 9.56947x& \cellcolor[rgb]{0.9990234375,0.7568359375,0.75} 9.78032x& \cellcolor[rgb]{0.9990234375,0.75,0.75} 21.68320x& \cellcolor[rgb]{0.9990234375,0.75,0.75} 21.71900x\\
256 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 598859& \cellcolor[rgb]{0.9990234375,0.935546875,0.75} 4.01075x& \cellcolor[rgb]{0.9990234375,0.927734375,0.75} 4.27823x& \cellcolor[rgb]{0.9990234375,0.935546875,0.75} 4.01290x& \cellcolor[rgb]{0.9990234375,0.927734375,0.75} 4.27501x& \cellcolor[rgb]{0.9990234375,0.75,0.75} 11.53833x& \cellcolor[rgb]{0.9990234375,0.75,0.75} 11.80069x& \cellcolor[rgb]{0.9990234375,0.75,0.75} 26.47159x& \cellcolor[rgb]{0.9990234375,0.75,0.75} 26.47409x\\
512 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 1054540& \cellcolor[rgb]{0.9990234375,0.923828125,0.75} 4.40890x& \cellcolor[rgb]{0.9990234375,0.9140625,0.75} 4.70502x& \cellcolor[rgb]{0.9990234375,0.923828125,0.75} 4.40897x& \cellcolor[rgb]{0.9990234375,0.9140625,0.75} 4.70366x& \cellcolor[rgb]{0.9990234375,0.75,0.75} 12.93893x& \cellcolor[rgb]{0.9990234375,0.75,0.75} 13.22190x& \cellcolor[rgb]{0.9990234375,0.75,0.75} 29.86374x& \cellcolor[rgb]{0.9990234375,0.75,0.75} 29.85531x\\
1024 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 1989472& \cellcolor[rgb]{0.9990234375,0.91796875,0.75} 4.59073x& \cellcolor[rgb]{0.9990234375,0.908203125,0.75} 4.90795x& \cellcolor[rgb]{0.9990234375,0.91796875,0.75} 4.59569x& \cellcolor[rgb]{0.9990234375,0.908203125,0.75} 4.90336x& \cellcolor[rgb]{0.9990234375,0.75,0.75} 13.62511x& \cellcolor[rgb]{0.9990234375,0.75,0.75} 13.93164x& \cellcolor[rgb]{0.9990234375,0.75,0.75} 31.53197x& \cellcolor[rgb]{0.9990234375,0.75,0.75} 31.56367x\\
2048 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 3831949& \cellcolor[rgb]{0.9990234375,0.9130859375,0.75} 4.73191x& \cellcolor[rgb]{0.9990234375,0.9033203125,0.75} 5.05794x& \cellcolor[rgb]{0.9990234375,0.9130859375,0.75} 4.73420x& \cellcolor[rgb]{0.9990234375,0.9033203125,0.75} 5.05587x& \cellcolor[rgb]{0.9990234375,0.75,0.75} 14.10539x& \cellcolor[rgb]{0.9990234375,0.75,0.75} 14.41266x& \cellcolor[rgb]{0.9990234375,0.75,0.75} 32.69551x& \cellcolor[rgb]{0.9990234375,0.75,0.75} 32.72633x\\
4096 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 7524589& \cellcolor[rgb]{0.9990234375,0.9111328125,0.75} 4.80394x& \cellcolor[rgb]{0.9990234375,0.9013671875,0.75} 5.13065x& \cellcolor[rgb]{0.9990234375,0.9111328125,0.75} 4.80706x& \cellcolor[rgb]{0.9990234375,0.9013671875,0.75} 5.13594x& \cellcolor[rgb]{0.9990234375,0.75,0.75} 14.33546x& \cellcolor[rgb]{0.9990234375,0.75,0.75} 14.66333x& \cellcolor[rgb]{0.9990234375,0.75,0.75} 33.25560x& \cellcolor[rgb]{0.9990234375,0.75,0.75} 33.30167x\\
8192 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 14901775& \cellcolor[rgb]{0.9990234375,0.91015625,0.75} 4.84418x& \cellcolor[rgb]{0.9990234375,0.8994140625,0.75} 5.18112x& \cellcolor[rgb]{0.9990234375,0.91015625,0.75} 4.84423x& \cellcolor[rgb]{0.9990234375,0.8994140625,0.75} 5.18259x& \cellcolor[rgb]{0.9990234375,0.75,0.75} 14.46452x& \cellcolor[rgb]{0.9990234375,0.75,0.75} 14.78932x& \cellcolor[rgb]{0.9990234375,0.75,0.75} 33.58380x& \cellcolor[rgb]{0.9990234375,0.75,0.75} 33.61478x\\
\caption{\label{tab:sha256}Benchmark of \texttt{benches/sha256.ll} output by \mintinline{bash}{dune exec bench -- -f sha256 -n 256}}

@@

Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Tellus at urna condimentum mattis. Enim facilisis gravida neque convallis. Enim facilisis gravida neque convallis a cras semper auctor. Vitae proin sagittis nisl rhoncus mattis rhoncus urna neque. Justo nec ultrices dui sapien eget mi proin. Id aliquet risus feugiat in ante. A cras semper auctor neque vitae tempus quam pellentesque nec. Nulla porttitor massa id neque aliquam vestibulum morbi. Facilisi cras fermentum odio eu. Odio pellentesque diam volutpat commodo sed egestas egestas fringilla. Amet consectetur adipiscing elit duis tristique sollicitudin nibh sit amet. Adipiscing at in tellus integer feugiat. A pellentesque sit amet porttitor. Sed elementum tempus egestas sed sed risus pretium quam. Quam viverra orci sagittis eu volutpat odio facilisis mauris sit. Arcu dictum varius duis at. Sociis natoque penatibus et magnis dis parturient montes. Varius sit amet mattis vulputate enim nulla aliquet. Ac ut consequat semper viverra. Scelerisque eleifend donec pretium vulputate sapien nec. Orci ac auctor augue mauris augue. Pulvinar mattis nunc sed blandit. Semper auctor neque vitae tempus quam pellentesque nec nam. Risus pretium quam vulputate dignissim. Dui faucibus in ornare quam viverra orci sagittis eu volutpat. Ac tortor vitae purus faucibus. Eu mi bibendum neque egestas congue quisque egestas diam in. Curabitur vitae nunc sed velit dignissim sodales ut eu sem. Arcu odio ut sem nulla.
